### 2021-04-02 input/proposal.tex
rework scoped broadcast

@@

In this section, we introduce model and notations to provide a general
definition of scoped broadcast in distributed systems.  Distributed
systems such as Edge infrastructures comprise heterogeneous machines
interconnected by communication links. We do not consider byzantine
processes.

@@

Processes can send messages to their neighboring processes. Processes
can reliably broadcast messages by forwarding delivered
messages~\cite{hadzilacos1994modular,nedelec2018causal,raynal2013distributed}. However,
uniform reliable broadcast states that \emph{all} correct processes
must deliver broadcast messages. This proves costly in large scale
systems comprising thousands of processes. Instead, we define
\emph{scoped broadcast} where messages reach only interested
processes, significantly reducing generated traffic.

\begin{definition}[\label{def:scoped}\underline{S}coped broad\underline{cast} (\NAMEB)]
  When Process $x$ scoped \underline{b}roadcasts $b_x(m)$ a
  \underline{m}essage $m$, every correct Process $y$ within a scope
  \underline{r}eceives $r_y(m)$ and \underline{d}elivers it
  $d_y(m)$. The scope depends on \underline{s}tates $\sigma$ of
  processes, \underline{m}etadata $\mu$ within received messages, and
  a \underline{p}redicate $\phi$ verified from process to process:
  $b_x(m) \wedge r_y(m) \implies \exists \pi_{xy} : \forall z \in
  \pi_{xy}, \phi(\mu_z, \sigma_z)$.
\end{definition}

This definition highlights the transitive relevance of messages and
encompasses more specific definitions of related
work~\cite{hsiao2005scoped,lue2006scoped,wang2015prodiluvian}.  A
process from Paris could scoped broadcast a message to all processes
in this city. A process from Paris could scoped broadcast a message to
all processes in this city plus neighboring cities by overloading
forwarded messages the first time they reach another city. Similarly
to reliable broadcast, scoped broadcast implementations expose
different trade-offs on space, time, and communication. In this paper,
we introduce an adaptive scoped broadcast the cost of which actually
depends on its operations, and the current scopes that exist in the
system.

%% \begin{definition}[S-broadcast properties]
%%   S-broadcast guarantees 3 properties:
%%   \begin{inparaenum}[(i)]
%%   \item Validity: If a correct process broadcasts a message, it
%%     eventually delivers it;
%%   \item Scoped Agreement: If a process broadcasts a message, then all
%%     correct processes within the scope eventually delivers it;
%%   \item Scoped Integrity: A process delivers a message only if it was
%%     previously broadcast within the scope.
%%   \end{inparaenum}
%% \end{definition}

@@

\input{input/figadd.tex} %% positioning (belong to problem & motivation)

@@

Finally, as stated in Theorem~\ref{theo:dcp}, dynamic consistent
partitioning not only requires the removal of all stale partitions,
but also the retrieval of the best up-to-date partitions. In that
regard, $\delta$'s have dual use: since they already reach borders of
partitions when they remove stale control informations, they also
trigger a competition when reaching such bordering processes (see
Line~\ref{line:compete}). This simply consists in sending the current
partition through the communication link from which the process
received the $\delta$. Upon receipt of this answer, processes act
normally by propagating their changes when they improve. These adds
fill the gaps left open by deletes.

>>>>

%% to better adapt positioning (I expect 2.5 pages
%% intro+related work)
\newpage

@@

Scoped broadcast is a communication primitive that propagates a
message around its broadcaster within an application-dependant scope.
For instance, a process from Paris could scoped broadcast messages to
all processes in Paris; and processes from other cities would never
deliver such messages. Scoped broadcast allows its implementations to
reduce generated traffic compared to uniform reliable
broadcast~\cite{hadzilacos1994modular, raynal2013distributed}, for
message propagation can stop as soon as messages reach the borders of
the scope.  This section introduces model and notations to provide a
general definition of scoped broadcast in distributed
systems. \TODO{to help understand adaptive scoped broadcast :).}
\TODO{Better transition to the rest of this section.}

Distributed systems such as Edge infrastructures comprise
heterogeneous machines interconnected by communication links. We do
not consider byzantine processes.

@@

Processes can send messages to their neighboring processes. Processes
can reliably broadcast messages by forwarding delivered
messages~\cite{birman1999bimodal, hadzilacos1994modular,
  nedelec2018causal, raynal2013distributed}. However, uniform reliable
broadcast states that \emph{all} correct processes must deliver
broadcast messages. This proves costly in large scale systems
comprising thousands of processes. Instead, we define \emph{scoped
broadcast} where messages reach only interested processes,
significantly reducing generated traffic.

\begin{definition}[\label{def:scoped}\underline{S}coped broad\underline{cast} (\NAMEB)]
  When Process $x$ scoped \underline{b}roadcasts $b_x(m)$ a
  \underline{m}essage $m$, every correct Process $y$ within a scope
  \underline{r}eceives $r_y(m)$ and \underline{d}elivers it
  $d_y(m)$. The scope depends on the \underline{s}tate $\sigma$ of
  each process, the \underline{m}etadata $\mu$ piggybacked by each
  message, and a \underline{p}redicate $\phi$ verified from process to
  process: $b_x(m) \wedge r_y(m) \implies \exists \pi_{xy}: \forall z
  \in \pi_{xy}, \phi(\mu_z, \sigma_z)$.
\end{definition}

This definition highlights the transitive relevance of messages and
encompasses more specific definitions of related
work~\cite{hsiao2005scoped, lue2006scoped, wang2015prodiluvian}. For
instance, a process from Paris could scoped broadcast messages to all
processes in Paris. This requires processes to know the city they are
in. In another instance, a process from Paris could scoped broadcast
messages to all processes in Paris plus neighboring cities. This
requires processes to overload forwarded messages the first time they
reach another city. The predicate checks if messages already reached
two distinct cities before delivery. Similarly to uniform reliable
broadcast, scoped broadcast implementations expose different
trade-offs on space, time, and communication.

Next Section introduces an adaptive scoped broadcast where the state
of each process is dynamic and changes depending all distinct scopes
that exist in the system.

% the cost of
% which actually depends on its operations, and the current scopes that
% exist in the system.

@@

\input{input/figadd.tex}

@@

Finally, as stated in Theorem~\ref{theo:dcp}, dynamic consistent
partitioning not only requires the removal of all stale partitions,
but also the retrieval of the best up-to-date partitions. In that
regard, $\delta$'s have dual use: since they already reach borders of
partitions when they remove stale control information, they also
trigger a competition when reaching such bordering processes (see
Line~\ref{line:compete}). This simply consists in sending the current
partition through the communication link from which the process
received the $\delta$. Upon receipt of this answer, processes act
normally by propagating their changes when they improve. These adds
fill the gaps left open by deletes.
